---
title: "| RESEARCH PROTOCOL\n| \n| Determining incidence rates and modifiable risk factors for infectious outcomes and medication adverse events in adult dermatomyositis patients through the OHDSI Community. \n"
fontsize: 12pt
geometry: margin=1in
output:
  bookdown::html_document2:
    df_print: paged
    toc: yes
    toc_depth: 2
    toc_float: yes
    number_sections: yes
    number_tables: yes
    css: style.css
  word_document:
    reference_docx: ohdsi-protocol-style.docx
  bookdown::pdf_document2:
    keep_tex: yes
    latex_engine: xelatex
    md_extensions: +raw_attribute
    number_sections: yes
    includes:
      before_body: title.tex
header-includes:
- \usepackage[numbers,sort&compress]{natbib}
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{caption}
- \usepackage{rotating}
- \usepackage{multirow}
- \usepackage{mwe,tikz}
- \usepackage[percent]{overpic}
- \usepackage{enumitem}
- \usepackage{hyperref}
- \newcolumntype{P}[1]{>{\raggedright\arraybackslash}p{#1}}
- \newcommand{\footerDate}{`r params$date`}
- \input{header.tex}
longtable: yes
mainfont: Arial
bibliography: Protocol.bib
params:
  date: '28-Mar-2023'
  version: 0.0.1
subtitle: 'Version: `r params$version`'
link-citations: yes
csl: bmj.csl
---

```{r setup, include=FALSE}

# install.packages("CirceR")

knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
options(kableExtra.latex.load_packages = FALSE)
library(kableExtra)
library(dplyr)
options(knitr.kable.NA = "")
options(knitr.table.format = function() {
  if (knitr::is_latex_output()) {
    "latex"
  } else if (knitr::is_html_output()) {
    "html"
  } else {
    "pipe"
  }
})

latex_table_font_size <- 8
```

# List of Abbreviations

```{r child = "Abbreviations.Rmd"}
```

\clearpage

# Responsible Parties

## Investigators

```{r child = "Investigators.Rmd"}
```

## Disclosures

This study is undertaken within Observational Health Data Sciences and Informatics (OHDSI), an open collaboration.[@ohdsi_ohdsi_2024]

Participating data owners will be responsible for self-reporting any grants funding the conversion and maintenance of their OMOP CDM.  Disclosures will be reported in accordance with publication policies of journals papers are submitted to. No other disclosures reported.

\clearpage

# Abstract

```{r child = "Abstract.Rmd"}
```

\clearpage

# Amendments and Updates

```{r amendments, echo=FALSE}
# amendments <- readr::read_delim(col_names = TRUE, delim = ";", trim_ws = TRUE, show_col_types = FALSE, file = "
#   Number; Date; Section of study protocol; Amendment or update; Reason
# ")
# 
# tab <- kable(amendments, booktabs = TRUE, linesep = "")
# 
# if (knitr::is_latex_output()) {
#   tab %>% kable_styling(latex_options = c("striped", "hold_position"), font_size = latex_table_font_size)
# } else {
#   tab %>% kable_styling(bootstrap_options = "striped")
# }
```

# Milestones

```{r dates, echo=FALSE}
dates <- readr::read_delim(col_names = TRUE, delim = ";", trim_ws = TRUE, show_col_types = FALSE, file = "

")

tab <- kable(dates, booktabs = TRUE, linesep = "")

if (knitr::is_latex_output()) {
  tab %>% kable_styling(latex_options = c("striped", "hold_position"), font_size = latex_table_font_size)
} else {
  tab %>% kable_styling(bootstrap_options = "striped")
}
```


```{r child = "MainText.Rmd"}
```


\clearpage

# References {-}

<div id="refs"></div>

\clearpage

\centerline{\Huge Appendix}

# (APPENDIX) Appendix {-}

# Exposure Cohort Definitions

```{r appendix,  echo=FALSE, results="asis", warning=FALSE, message=FALSE}
# source("https://raw.githubusercontent.com/ohdsi-studies/LegendT2dm/master/R/PrettyOutput.R")
# 
# printCohortDefinitionFromNameAndJson(name = "Template Cohort (New-users of DDP4 inhibitors)",
#                                      json = SqlRender::readSql("templateCohort.json"),
#                                      withConcepts = TRUE)
```

# Outcome Cohort Definitions

# Negative Control Concepts {#negative-controls}
